\documentclass[letterpaper,11pt]{article}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-11pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}\vspace{5pt}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape ANANDU B S} \\ \vspace{1pt}
    101 Vinayaka Enclave, 7th Cross Road, Neeladri Nagar, Electronic City, Bengaluru, Karnataka 560100 \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +91 8921294138  ~ \href{mailto:x@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{anandubs1409@gmail.com}} ~ 
    \href{https://linkedin.com/in/nithinsv}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/anandu-bs}}  ~
    \href{https://github.com/}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/ananduv2}}
    \vspace{-8pt}
\end{center}

\section{Professional Summary}
\resumeSubHeadingListStart
  \resumeSubItem{Bangalore-based DevOps and cloud engineer with 5+ years if experience delivering production infrastructure, observability, backend services and automation for AI media platforms. I work primarily with AWS and GCP, build scalable monitoring systems, run GPU-backed workloads, and deliver resilient deployments with custom autoscaling for long-running GenAI pipelines. I was also the point of contact for implementing SOC 2 compliance across infrastructure and operations workflows.}
\resumeSubHeadingListEnd
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Computer Application }{Kollam, Kerala}
      {Tkm College of Engineering, Kollam }{Aug. '19 -- May '21}
  \resumeSubHeadingListEnd
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bachelor of Computer Applications }{Kollam, Kerala}
      {UIT Mukhathala, Kollam}{Jun. '16 -- Apr '19}
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}

\begin{tabularx}{\textwidth}{@{}>{\bfseries}p{3cm}X@{}}
Languages & Python, Bash/Shell Scripting, SQL, HTML, CSS \\
Cloud & AWS, Google Cloud Platform (GCP) \\
Tools & Docker, Kubernetes, Jenkins, Terraform, Linux, Git, Nginx, Prometheus, Grafana \\
Concepts & CI/CD, DevOps, MLOps, Microservices, Agile \\
\end{tabularx}





%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
      {DevOps Engineer II $|$ \emph{Full-time }}{March 2025 -- Present}
      {NeuralGarage Pvt Ltd}{Bangalore}
      \resumeItemListStart
      \resumeItem{Sole owner of the organization's cloud infrastructure, platform operations, security initiatives, and DevOps strategy.}
      \resumeItem{Designed and managed multi-cloud infrastructure across AWS, GCP, and on-premises environments supporting AI/ML product development and production workloads.}
      \resumeItem{Led infrastructure architecture, network design, and GPU cluster management for research and production environments.}
      \resumeItem{Established and maintained organization-wide monitoring, alerting, observability, and security monitoring frameworks.}
      \resumeItem{Directed SOC 2 compliance initiatives, implementing security controls, access management policies, and operational governance procedures.}
      \resumeItem{Evaluated cloud providers, infrastructure services, and third-party vendors to optimize scalability, reliability, and operational costs.}
      \resumeItem{Managed client-facing technical discussions and coordinated outsourced teams responsible for quality assurance and operational processes.}
      \resumeItem{Collaborated with engineering leadership to define infrastructure roadmaps, deployment standards, and platform reliability objectives.}
      \resumeItemListEnd
% --------------
    \resumeSubheading
      {DevOps Engineer $|$ \emph{Full-time }}{Dec 2022 -- Mar 2025}
      {NeuralGarage}{Bangalore}
      \resumeItemListStart
\resumeItem{Designed and maintained CI/CD pipelines, automating application deployment, infrastructure provisioning, and release workflows across development, staging, and production environments.}
\resumeItem{Implemented and managed cloud infrastructure across AWS and GCP environments supporting multiple products and internal services.}
\resumeItem{Built and maintained secure VPN connectivity between cloud and on-premises environments to support distributed infrastructure operations.}
\resumeItem{Developed custom automation tools and infrastructure management scripts to streamline provisioning, deployment, monitoring, and operational workflows.}
\resumeItem{Designed and maintained Grafana dashboards, monitoring systems, and alerting frameworks providing visibility into application and infrastructure health.}
\resumeItem{Performed infrastructure security assessments, server hardening, access control management, and operational maintenance activities.}
\resumeItem{Managed GPU-enabled compute environments and supported infrastructure requirements for machine learning and AI workloads.}
\resumeItem{Collaborated with backend engineering teams in developing FastAPI-based services and internal platform tooling.}
\resumeItem{Developed reusable Python packages and utilities to simplify project initialization, deployment, and operational processes.}
\resumeItem{Managed Linux-based production environments and optimized cloud resources across AWS services including EC2, S3, EFS, and networking components.}
\resumeItemListEnd
    \resumeSubheading
      {Software Engineer $|$ \emph{Full-time }}{Sep 2021 -- Dec 2022}
      {Gemini Solutions Pvt Ltd}{Panchkula}
      \resumeItemListStart
        \resumeItem{Developed and maintained complex client-side applications using Angular and React, focusing on performance optimization and dynamic user experiences. }
        \resumeItem{Worked on API integrations and data visualization to present actionable insights for users in real-time.}
        \resumeItem{Optimized the frontend performance through lazy loading, code splitting, and minification techniques, improving page load times and overall application responsiveness.}
        \resumeItem{Collaborated with cross-functional teams, including design and product teams, to translate business requirements into technical solutions.}
        \resumeItem{Contributed to the development of scalable and maintainable code, following best practices in component design and state management.}
        \resumeItem{Redesigned the UI of a database migration application within 3 months, improving usability and streamlining the user experience.}
        \resumeItem{Developed an application for monitoring Azure usage stats, providing real-time insights and analytics on cloud resource consumption}
        \resumeItem{Owned and completed a major module in a complex project, involving transactions and ensuring consistency and reliability of transactional operations.}
        \resumeItem{Made a major contribution to revamping the UI from PHP to Angular, enhancing the overall user experience and improving maintainability of the application.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  \resumeSubHeadingListStart
    \resumeSubheading
      {Associate System Engineer$|$ \emph{Full-time }}{Apr 2021 -- Sep 2021}
      {Teqstories Pvt Ltd}{Bangalore}
      \resumeItemListStart
    \resumeItem{Designed and developed software solutions for both internal stakeholders and external clients across multiple business domains.}
    \resumeItem{Managed application deployment, monitoring, and operational support across cloud-based environments.}
    \resumeItem{Mentored interns and delivered technical training sessions on software development and industry best practices.}
    \resumeItem{Collaborated with clients to gather requirements, define project scope, and translate business needs into technical solutions.}
\resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-16pt}

 \section{Certifications}
 \resumeSubHeadingListStart
    \resumeSubheading
      {AWS Certified Cloud Practitioner }{Dec 2021}
      {Issued by AWS - Registration ID-\href{https://anandubs-resume.netlify.app/AWS\%20Certified\%20Cloud\%20Practitioner.pdf}{423773593} }{}
  \resumeSubHeadingListEnd
  \resumeSubHeadingListStart
    \resumeSubheading
      {AWS Cloud Technical Essentials}{May 2021}
      {Issued by Coursera  - \href{https://coursera.org/share/cae4c1950b1749313ee111e4874aae79}{https://coursera.org/share/cae4c1950b1749313ee111e4874aae79}}{}
  \resumeSubHeadingListEnd
  \resumeSubHeadingListStart
    \resumeSubheading
      {Programming for Everybody (Getting Started with Python)}{May 2020}
      {Issued by Coursera - https://coursera.org/share/982a69546fb228fa2817817b24c83175\href{https://coursera.org/share/982a69546fb228fa2817817b24c83175} }{}
  \resumeSubHeadingListEnd
   \resumeSubHeadingListStart
    \resumeSubheading
      {AWS S3 Basics }{May 2021}
      {Issued by Coursera - https://coursera.org/share/ec46f202d3ac0d862cf688fdff599a5d\href{https://coursera.org/share/ec46f202d3ac0d862cf688fdff599a5d} }{}
  \resumeSubHeadingListEnd
  
%

\section{Languages}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    
     \textbf{English, Malayalam, Tamil}  \\
     \vspace{2pt}
       
    }}
 \end{itemize}
 % \vspace{-1pt}

\section{Declaration}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    
     \text{I do hereby declare that all the information furnished above is true to the best of my knowledge and belief.}  \\
     \begin{flushright}
        \textbf{Anandu B S}
     
     \end{flushright}
     \vspace{2pt}
       
    }}
 \end{itemize}

 


\end{document}